---
title: "Bachelorproef dataverwerking"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Remark:** Before running this code in RStudio, first do (from the menu): *Session > Set Working Directory > To Source File Location*. This allows loading the .csv file from the current directory.

## Load data
```{r}
# Load data from csv
startup <- read.csv("./CSV/Combined-StartupResults.csv", sep = ",")
startupCake <- startup[startup$Project == 'Cake',]
startupMindustry <- startup[startup$Project == 'Mindustry',]    

search <- read.csv("./CSV/Combined-SearchResults.csv", sep = ",")
searchCake <- search[search$Project == 'Cake',]
searchMindustry <- search[search$Project == 'Mindustry',]   

build <- read.csv("./CSV/Combined-BuildResults.csv", sep = ",")
buildCake <- build[build$Project == 'Cake',]

profile <- read.csv("./CSV/Combined-ProfileResults.csv", sep = ",")
profileCake <- profile[profile$Project == 'Cake',]
profileMindustry <- profile[profile$Project == 'Mindustry',]
```

## Startup
```{r}
startupVsCodeCake <- startupCake[startupCake$Program == 'VSCode',]
startupVsCodeMindustry <- startupMindustry[startupMindustry$Program == 'VSCode',]

startupVisualStudioCake <- startupCake[startupCake$Program == 'VisualStudio',]

startupEclipseCake <- startupCake[startupCake$Program == 'Eclipse',]
startupEclipseMindustry <- startupMindustry[startupMindustry$Program == 'Eclipse',]

startupNotepadCake <- startupCake[startupCake$Program == 'Notepad',]
startupNotepadMindustry <- startupMindustry[startupMindustry$Program == 'Notepad',]

startupIntelliJMindustry <- startupMindustry[startupMindustry$Program == 'IntelliJ',]
```

### Startup Cake
```{r}
summary(startupVsCodeCake$StartupTime.ms.)  # min, max, kwartielen, gemiddelde
sd(startupVsCodeCake$StartupTime.ms.)       # standaardafwijking (formule voor steekproef)

summary(startupVisualStudioCake$StartupTime.ms.)  # min, max, kwartielen, gemiddelde
sd(startupVisualStudioCake$StartupTime.ms.)       # standaardafwijking (formule voor steekproef)

summary(startupEclipseCake$StartupTime.ms.)  # min, max, kwartielen, gemiddelde
sd(startupEclipseCake$StartupTime.ms.)       # standaardafwijking (formule voor steekproef)

summary(startupNotepadCake$StartupTime.ms.)  # min, max, kwartielen, gemiddelde
sd(startupNotepadCake$StartupTime.ms.)       # standaardafwijking (formule voor steekproef)
```

### Startup Mindustry
```{r}
summary(startupVsCodeMindustry$StartupTime.ms.)  # min, max, kwartielen, gemiddelde
sd(startupVsCodeMindustry$StartupTime.ms.)       # standaardafwijking (formule voor steekproef)

summary(startupEclipseMindustry$StartupTime.ms.)  # min, max, kwartielen, gemiddelde
sd(startupEclipseMindustry$StartupTime.ms.)       # standaardafwijking (formule voor steekproef)

summary(startupNotepadMindustry$StartupTime.ms.)  # min, max, kwartielen, gemiddelde
sd(startupNotepadMindustry$StartupTime.ms.)       # standaardafwijking (formule voor steekproef)

summary(startupIntelliJMindustry$StartupTime.ms.)  # min, max, kwartielen, gemiddelde
sd(startupIntelliJMindustry$StartupTime.ms.)       # standaardafwijking (formule voor steekproef)
```

## Search
```{r}
searchVsCodeCake <- searchCake[searchCake$Program == 'VSCode',]
searchVsCodeMindustry <- searchMindustry[searchMindustry$Program == 'VSCode',]

searchVisualStudioCake <- searchCake[searchCake$Program == 'VisualStudio',]

searchEclipseCake <- searchCake[searchCake$Program == 'Eclipse',]
searchEclipseMindustry <- searchMindustry[searchMindustry$Program == 'Eclipse',]

searchNotepadCake <- searchCake[searchCake$Program == 'Notepad',]
searchNotepadMindustry <- searchMindustry[searchMindustry$Program == 'Notepad',]

searchIntelliJMindustry <- searchMindustry[searchMindustry$Program == 'IntelliJ',]
```

### Search Cake
```{r}
summary(searchVsCodeCake$SearchTime.ms.)  # min, max, kwartielen, gemiddelde
sd(searchVsCodeCake$SearchTime.ms.)       # standaardafwijking (formule voor steekproef)

summary(searchVisualStudioCake$SearchTime.ms.)  # min, max, kwartielen, gemiddelde
sd(searchVisualStudioCake$SearchTime.ms.)       # standaardafwijking (formule voor steekproef)

summary(searchEclipseCake$SearchTime.ms.)  # min, max, kwartielen, gemiddelde
sd(searchEclipseCake$SearchTime.ms.)       # standaardafwijking (formule voor steekproef)

summary(searchNotepadCake$SearchTime.ms.)  # min, max, kwartielen, gemiddelde
sd(searchNotepadCake$SearchTime.ms.)       # standaardafwijking (formule voor steekproef)
```

### Search Mindustry
```{r}
summary(searchVsCodeMindustry$SearchTime.ms.)  # min, max, kwartielen, gemiddelde
sd(searchVsCodeMindustry$SearchTime.ms.)       # standaardafwijking (formule voor steekproef)

summary(searchEclipseMindustry$SearchTime.ms.)  # min, max, kwartielen, gemiddelde
sd(searchEclipseMindustry$SearchTime.ms.)       # standaardafwijking (formule voor steekproef)

summary(searchNotepadMindustry$SearchTime.ms.)  # min, max, kwartielen, gemiddelde
sd(searchNotepadMindustry$SearchTime.ms.)       # standaardafwijking (formule voor steekproef)

summary(searchIntelliJMindustry$SearchTime.ms.)  # min, max, kwartielen, gemiddelde
sd(searchIntelliJMindustry$SearchTime.ms.)       # standaardafwijking (formule voor steekproef)
```

## Build
```{r}
buildVsCodeCake <- buildCake[buildCake$Program == 'VSCode',]

buildVisualStudioCake <- buildCake[buildCake$Program == 'VisualStudio',]

buildEclipseCake <- buildCake[buildCake$Program == 'Eclipse',]
```

### Build Cake
```{r}
summary(buildVsCodeCake$BuildTime.ms.)  # min, max, kwartielen, gemiddelde
sd(buildVsCodeCake$BuildTime.ms.)       # standaardafwijking (formule voor steekproef)

summary(buildVisualStudioCake$BuildTime.ms.)  # min, max, kwartielen, gemiddelde
sd(buildVisualStudioCake$BuildTime.ms.)       # standaardafwijking (formule voor steekproef)

summary(buildEclipseCake$BuildTime.ms.)  # min, max, kwartielen, gemiddelde
sd(buildEclipseCake$BuildTime.ms.)       # standaardafwijking (formule voor steekproef)
```

## Profile
```{r}
profileVsCodeCake <- profileCake[profileCake$Program == 'VSCode',]
profileVsCodeMindustry <- profileMindustry[profileMindustry$Program == 'VSCode',]

profileVisualStudioCake <- profileCake[profileCake$Program == 'VisualStudio',]

profileEclipseCake <- profileCake[profileCake$Program == 'Eclipse',]
profileEclipseMindustry <- profileMindustry[profileMindustry$Program == 'Eclipse',]

profileNotepadCake <- profileCake[profileCake$Program == 'Notepad',]
profileNotepadMindustry <- profileMindustry[profileMindustry$Program == 'Notepad',]

profileIntelliJMindustry <- profileMindustry[profileMindustry$Program == 'IntelliJ',]
```

### Profile Cake CPU
```{r}
summary(profileVsCodeCake$CPU...)  # min, max, kwartielen, gemiddelde
sd(profileVsCodeCake$CPU...)       # standaardafwijking (formule voor steekproef)

summary(profileVisualStudioCake$CPU...)  # min, max, kwartielen, gemiddelde
sd(profileVisualStudioCake$CPU...)       # standaardafwijking (formule voor steekproef)

summary(profileEclipseCake$CPU...)  # min, max, kwartielen, gemiddelde
sd(profileEclipseCake$CPU...)       # standaardafwijking (formule voor steekproef)

summary(profileNotepadCake$CPU...)  # min, max, kwartielen, gemiddelde
sd(profileNotepadCake$CPU...)       # standaardafwijking (formule voor steekproef)
```

### Profile Mindustry CPU
```{r}
summary(profileVsCodeMindustry$CPU...)  # min, max, kwartielen, gemiddelde
sd(profileVsCodeMindustry$CPU...)       # standaardafwijking (formule voor steekproef)

summary(profileEclipseMindustry$CPU...)  # min, max, kwartielen, gemiddelde
sd(profileEclipseMindustry$CPU...)       # standaardafwijking (formule voor steekproef)

summary(profileNotepadCake$CPU...)  # min, max, kwartielen, gemiddelde
sd(profileNotepadCake$CPU...)       # standaardafwijking (formule voor steekproef)

summary(profileIntelliJMindustry$CPU...)  # min, max, kwartielen, gemiddelde
sd(profileIntelliJMindustry$CPU...)       # standaardafwijking (formule voor steekproef)
```

### Profile Cake Ram
```{r}
summary(profileVsCodeCake$RAM.MB.)  # min, max, kwartielen, gemiddelde
sd(profileVsCodeCake$RAM.MB.)       # standaardafwijking (formule voor steekproef)

summary(profileVisualStudioCake$RAM.MB.)  # min, max, kwartielen, gemiddelde
sd(profileVisualStudioCake$RAM.MB.)       # standaardafwijking (formule voor steekproef)

summary(profileEclipseCake$RAM.MB.)  # min, max, kwartielen, gemiddelde
sd(profileEclipseCake$RAM.MB.)       # standaardafwijking (formule voor steekproef)

summary(profileNotepadCake$RAM.MB.)  # min, max, kwartielen, gemiddelde
sd(profileNotepadCake$RAM.MB.)       # standaardafwijking (formule voor steekproef)
```

### Profile Mindustry Ram
```{r}
summary(profileVsCodeMindustry$RAM.MB.)  # min, max, kwartielen, gemiddelde
sd(profileVsCodeMindustry$RAM.MB.)       # standaardafwijking (formule voor steekproef)

summary(profileEclipseMindustry$RAM.MB.)  # min, max, kwartielen, gemiddelde
sd(profileEclipseMindustry$RAM.MB.)       # standaardafwijking (formule voor steekproef)

summary(profileNotepadMindustry$RAM.MB.)  # min, max, kwartielen, gemiddelde
sd(profileNotepadMindustry$RAM.MB.)       # standaardafwijking (formule voor steekproef)

summary(profileIntelliJMindustry$RAM.MB.)  # min, max, kwartielen, gemiddelde
sd(profileIntelliJMindustry$RAM.MB.)       # standaardafwijking (formule voor steekproef)
```

## Combined Averages
## Startup
```{r}
mean(append(startupVsCodeCake$StartupTime.ms., startupVsCodeMindustry$StartupTime.ms.))  
mean(startupVisualStudioCake$StartupTime.ms.)  
mean(append(startupEclipseCake$StartupTime.ms., startupEclipseMindustry$StartupTime.ms.))
mean(append(startupNotepadCake$StartupTime.ms., startupNotepadMindustry$StartupTime.ms.))
mean(startupIntelliJMindustry$StartupTime.ms.)  
```

### Search
```{r}
mean(append(searchVsCodeCake$SearchTime.ms., searchVsCodeMindustry$SearchTime.ms.))  
mean(searchVisualStudioCake$SearchTime.ms.)  
mean(append(searchEclipseCake$SearchTime.ms., searchEclipseMindustry$SearchTime.ms.))
mean(append(searchNotepadCake$SearchTime.ms., searchNotepadMindustry$SearchTime.ms.))
mean(searchIntelliJMindustry$SearchTime.ms.)  
```

#### Build
```{r}
mean(buildVsCodeCake$BuildTime.ms.)  
mean(buildVisualStudioCake$BuildTime.ms.)  
mean(buildEclipseCake$BuildTime.ms.)
```

### CPU
```{r}
mean(append(profileVsCodeCake$CPU..., profileVsCodeMindustry$CPU...))  
mean(profileVisualStudioCake$CPU...)  
mean(append(profileEclipseCake$CPU..., profileEclipseMindustry$CPU...))
mean(append(profileNotepadCake$CPU..., profileNotepadMindustry$CPU...))
mean(profileIntelliJMindustry$CPU...)  
```

### RAM
```{r}
mean(append(profileVsCodeCake$RAM.MB., profileVsCodeMindustry$RAM.MB.))  
mean(profileVisualStudioCake$RAM.MB.)  
mean(append(profileEclipseCake$RAM.MB., profileEclipseMindustry$RAM.MB.))
mean(append(profileNotepadCake$RAM.MB., profileNotepadMindustry$RAM.MB.))
mean(profileIntelliJMindustry$RAM.MB.)  
```

